\documentclass[a4paper, 10.75pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{xcolor}


\input{glyphtounicode}
\usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in} % odd side means left side
\addtolength{\evensidemargin}{-0.5in} % Ridgt side margin
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.70 in} % Default was -.5in
\addtolength{\textheight}{1.0in}

\urlstyle{same} 

% \raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-5pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Subsection formatting
\titleformat{\subsection}{
  \vspace{-4pt}\scshape\raggedright\large
}{\hspace{-.15in}}{0em}{}[\color{black}\vspace{-8pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

% -------------------- CUSTOM COMMANDS --------------------
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-8pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-8pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\setlength{\footskip}{4.08003pt}

% -------------------- START OF DOCUMENT --------------------
\begin{document}


\begin{center}
    \textbf{\Huge \scshape John Doe} \\ \vspace{8pt}
    \small 
    \textbf{\underline{Phone}}: {+91 1234567890} \hspace{12pt} % Adjust the value as needed
    \href{https://github.com/abhiphile}{\textbf{\underline{GitHub}}} \hspace{12pt} % Adjust the value as needed
    \href{https://www.linkedin.com/in/abhishek-kumar-nitdelhi/}{\textbf{\underline{Linkedin}}} \hspace{12pt} % Adjust the value as needed
    \textbf{\underline{Email}}: 
    \href{mailto:abhishek.nitdelhi@gmail.com}
    {\underline{abhishek.nitdelhi@gmail.com}} \hspace{12pt} 
    \href{https://abhishek-portfolio-chi.vercel.app/}{{\textbf{\underline{Portfolio}}}}
\end{center}


% -------------------- EDUCATION --------------------
\section{Education}
\resumeSubHeadingListStart

\resumeSubheading
{National Institute of Technology Delhi}{2021--2025}
{B.Tech in Electronics and Communication Engineering
$|$ Minor Degree in AI/ML}{CGPA: 7.88 /10}

\resumeSubheading
{New Horizon School Bhagalpur}{2018--2020}
{12th Grade}{Percentage: 96.2\%}

\resumeSubHeadingListEnd


% -------------------- SKILLS --------------------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
    
     \textbf{Languages/Database}{: C/C++, Python, JavaScript/TypeScript, HTML/CSS, MySQL} \\
     \textbf{Software \& Tools}{: Docker, Git/GitHub, VS Code, PyCharm, MATLAB}\\
      \textbf{Frameworks}{: React.js, Next.js} \\
      \textbf{Libraries}{: SymPy, Pandas, NumPy, Matplotlib, OpenCV, Manim, Tkinter }\\
     \textbf{Machine Learning Libraries}{: SciKit Learn, TensorFlow}
    }}
 \end{itemize}

 % -------------------- EXPERIENCE --------------------
\section{Work Experience}
\resumeSubHeadingListStart

    \resumeProjectHeading
    {\textbf{Google Summer of Code (GSoC) SymPy} $|$ \footnotesize\emph{Open source contributer}}{Remote $|$ \textnormal{May 2024 - Present}}
    \resumeItemListStart
        \resumeItem{\textbf{Improving Control module :} Contributed to the Control module by enhancing the \textbf{StateSpace} and \textbf{TransferFunction} classes, refactoring plots to use symbolic methods instead of numerical methods, and implementing new plot types.}
        \resumeItem{\textbf{Added Interconnection between StateSpace classes :} Enhanced StateSpace module by integrating \textbf{Series}, \textbf{Parallel}, and \textbf{Feedback} interconnections between \textbf{StateSpace} classes. Implemented symbolic solvers for \textbf{state vectors} and \textbf{output vectors}, boosting functionality.}
        \resumeItem{\textbf{Code Quality:} Ensured high code quality by implementing comprehensive tests, adhering to coding standards, and providing thorough documentation.}
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{VSAT Pvt. Ltd.} $|$ \footnotesize\emph{Web Development Intern}}{Remote $|$ \textnormal{June 2023 – July 2023 }}
    \resumeItemListStart
        \resumeItem{\textbf{Improving User Experience :} Elevated user experience by revamping the UI, ensuring better alignment, incorporating sliders, and creating informative 'About Us' \& 'Contact Us' pages using technologies like jQuery, Bootstrap classes, and JavaScript.}
        \resumeItem{Added a Quick Enquiry form with jQuery for validation, improved website responsiveness via Bootstrap, and integrated maps, driving improved user engagement and functionality.}
    \resumeItemListEnd

\resumeSubHeadingListEnd


% -------------------- PROJECTS --------------------
\section{Personal Projects}
\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{Musicly} $|$ \footnotesize\emph{Next JS, React, Tailwind CSS, Appwrite Cloud, TypeScript}}{{\href{https://musicly-lemon.vercel.app/}{\underline{Link} }$|$}{\href{https://github.com/abhishek-kuma/Musicly}{ \underline{Code}}}}
\resumeItemListStart
    \resumeItem{Engineered \textbf{Musicly}, a music app using \textbf{Next.js 14}, \textbf{React}, and \textbf{TypeScript}, providing a dynamic and responsive user experience.}
    \resumeItem{Leveraged \textbf{Appwrite Cloud} for \textbf{authentication}, \textbf{user song storage}, enabling users to \textbf{contribute their own songs}, and fostering community interaction through a \textbf{chat box}.}
    \resumeItem{Implemented \textbf{login and logout functionality} to enhance user privacy and overall experience.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{AutoResume} $|$ \footnotesize\emph{Python, CI/CD}}{\href{https://github.com/abhiphile/AutoResume}{\underline{Link}}}
\resumeItemListStart
    \resumeItem{Built an automated system using LaTeX and Python scripts to generate, compile, and distribute professional resumes. Included a CI/CD pipeline with GitHub Actions to streamline the process, ensuring efficient and error-free resume creation.}
    \resumeItem{Crafted seamless integration with Google Drive and Telegram using their respective APIs. Designed and developed functionalities to upload generated resumes to Google Drive and send both the file and its download link via a Telegram bot, providing real-time status updates.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Articlyfy} $|$ \footnotesize\emph{Next JS, React, Appwrite Cloud, TypeScript}}{{\href{https://articlify-henna.vercel.app/}{\underline{Link} }} $|$ \href{https://github.com/abhishek-kuma/Articlify_}{ \underline{Code}}}
\resumeItemListStart
    \resumeItem{Developed a feature-rich Next.js 14 website named Articlyfy, utilizing React for a dynamic frontend and TypeScript for robustness.}
    \resumeItem{Introduced complete authentication and database functionality using Appwrite Cloud, enabling seamless user authentication and article storage.}
\resumeItemListEnd


\resumeSubHeadingListEnd


\section{Coding Profiles}
\href{https://github.com/abhiphile}{\textbf{Github}}\ $|$ 
\href{https://leetcode.com/u/abhishek_nitdelhi/}{\textbf{Leetcode}}\ $|$ 
\href{https://www.codechef.com/users/abhi_nit_delhi/}{\textbf{CodeChef}}\ $|$ 
\href{https://codeforces.com/profile/AbhisheKr}{\textbf{Codeforces}}\ $|$

% -------------------- ACHIEVEMENTS --------------------
\section{Achievements}


\begin{itemize}[leftmargin=0.15in, label={}]
    \item Selected in \textbf{Google Summer of Code (GSoC) 2024}, standing out among \textbf{43,984} applicants from \textbf{172 countries} for contributions to open-source projects. \textbf{ Top 0.02\%}
    \item Acquired proficiency in advanced algorithms and data structures on LeetCode, attaining a rating of \textbf{1600+} and successfully solving \textbf{500+} questions.
    \item Secured a rank 32 in CodeRush coding competition.
\end{itemize}

\end{document}
